The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
nvm reorg, just fix \@ref{(fig:socres)}

@@

Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure 6a). Individual graph strength and layer relevance increased for
all summer layers as individuals became more connected with increasing window
lengths (Figure 6c, Figure 6d). These results suggest that an increasing window
length, especially for the summer season, may be resulting in less precisely
defined seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.

@@

@@

```{r, fig.cap='(ref:socres)'}
knitr::include_graphics('../graphics/figure-spatialthreshold.png')
```

>>>>

In general, individuals in multilayer networks became more connected as a
function of social scale, however, this relationship varied by habitat type and
season. As social scale increased, connective redundancy increased rapidly when
groups were formed based on ~100m threshold, followed by a plateau and slight
decrease at higher thresholds, presumably due to an increase in summer forest
degree at ~500m (Figure \@ref(fig:socres)b). Regardless of social scale, layer relevance did not
change for any habitat types or seasons, which suggests habitat-by-season layers
captured most, if not all, of the potential connections and individual would
have across all networks (Figure 3c). Finally, somewhat predictably, graph
strength for winter networks increased up to ~100-200m thresholds, followed by a
plateau, while graph strength for summer networks did not change as the social
threshold increased (Figure 3d).  Taken together, these results suggest the
optimal social scale at which groups should be assigned is likely somewhere
between ~20-100m based on the rate at which network metrics stabilized. For
ungulates, groups are often assigned based on 50m threshold (Lingle 2003;
Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
quantities of data, ~50m is likely an ideal social scale for generating social
networks in caribou and similar species.

@@

Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure 6a). Individual graph strength and layer relevance increased for
all summer layers as individuals became more connected with increasing window
lengths (Figure 6c, Figure 6d). These results suggest that an increasing window
length, especially for the summer season, may be resulting in less precisely
defined seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics. Similarly,

@@

Shifting window position results showed increasing layer similarity

@@

```{r socres, fig.cap='(ref:socres)'}
knitr::include_graphics('../graphics/figure-spatialthreshold.png')
```
